---
title: "碳排放管理對於企業股價之影響"
author: "Names _____"
date: "5/17/2022"
output: html_document
---
<style>
    body { background-color: #A9CAAB; }
    pre, pre:not([class]) { background-color: gainsboro; }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(readxl)
library(caret)
library(tidyverse)
library(rpart)
library(rpart.plot)
library(rsample) 
library(randomForest)
library(modelr)
library(corrplot)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(DT)

esg_df<- read_excel("data/ACWI-ESG-Results_1.xlsx")
esg_uni_df <-read_excel("data/ACWI-ESG-Universal-Results_1.xlsx")

# override the default setting of ggplot
theme_set(theme_minimal())
```

## 研究方法

利用MSCI ACWI Europe ESG Leaders Index 中的個股與其碳排管理指標，進行單因子迴歸分析，以探討「碳排管理是否能帶來超額報酬」之課題。由於產業間業務性質差異甚大，因此也會將個股按照產業區分，以達到產業中立之目的。

## 研究動機

分析師報告中證實MSCI ACWI ESG Leaders Index的確在2020年疫情爆發之後較MSCI ACWI Index取得相對好的報酬。近期歐盟祭出2050年碳中和目標與一系列政策，企業因此面臨低碳轉型風險，因此我們希望將樣本池鎖定歐盟企業，且著重於ESG中的碳排放管理指標，期許能夠針對這個課題得出一些新發現。

```{r data cleaning, echo=FALSE, warning=FALSE}
esg_eu_df = esg_df %>% filter(ISSUER_CNTRY_DOMICILE %in% c("AT", "BE", "BG", "HR", "CY", "DK", "EE", "FI", "FR", "DE", "GR", "HU", "IE", "IT", "LV", "LT", "LU", "MT", "NL", "PL","PT","RO", "SK", "SI", "ES", "SE"))

carb_heavy_df = esg_df %>% filter(Industry %in% c("Materials", "Utilities", "Energy", "Industrial"))

carb_light_df = esg_df %>% 
  filter(!Industry %in% c("Materials", "Utilities", "Energy", "Industrial")) 

# chnage "return" variables from character to double
carb_heavy_df[, c(31:33)] <- sapply(carb_heavy_df[, c(31:33)], as.numeric)
carb_light_df[, c(31:33)] <- sapply(carb_light_df[, c(31:33)], as.numeric)
esg_eu_df[, c(31:33)] <- sapply(esg_eu_df[, c(31:33)], as.numeric)

# split the data into train/test 
set.seed(100)
heavy_split = initial_split(carb_heavy_df, prop = 0.9)
heavy_train = training(heavy_split)
heavy_test = testing(heavy_split)

light_split = initial_split(carb_light_df, prop = 0.9)
light_train = training(light_split)
light_test = testing(light_split)

```


## 分析與結果

### Exploratory Data Analysis

(說明)



```{r eda, echo=FALSE, warning=FALSE, message=FALSE}
heavy.graph <- ggplot(carb_heavy_df, aes(x=CARBON_EMISSIONS_SCORE, y=TotalReturn_2y))+
  geom_point() + geom_smooth(method="lm", col="red") + ylim(-10, 1000)+ 
  ggtitle("Correlation of Emission Score to Return - Carbon Heavy Industries") + 
  labs(y = "Total Return Rate - 2 years", x = "Carbon Emission Score",) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

light.graph <- ggplot(carb_light_df, aes(x=CARBON_EMISSIONS_SCORE, y=TotalReturn_2y))+
  geom_point()+ geom_smooth(method="lm", col="red") + ylim(-10, 1000)+ 
  ggtitle("Correlation of Emission Score to Return - Carbon Light Industries") + 
  labs(y = "Total Return Rate - 2 years", x = "Carbon Emission Score",) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))


# map plot
map_eu = esg_eu_df %>%
  group_by(ISSUER_CNTRY_DOMICILE) %>%
  summarise(avg_score = mean(CARBON_EMISSIONS_SCORE))

map_eu$country = c("Austria","Belgium","Germany","Denmark","Spain","Finland","France","Greece","Hungry", "Ireland","Italy","Luxembourg","Netherlands","Poland","Portugal","Sweden")

world_map <- ne_countries(scale = 50, returnclass = 'sf')
european_union <- c("Austria","Belgium","Bulgaria","Croatia","Cyprus",
                    "Czech Rep.","Denmark","Estonia","Finland","France",
                    "Germany","Greece","Hungary","Ireland","Italy","Latvia",
                    "Lithuania","Luxembourg","Malta","Netherlands","Poland",
                    "Portugal","Romania","Slovakia","Slovenia","Spain",
                    "Sweden","United Kingdom")

european_union_map <- world_map %>% 
  filter(name %in% european_union)

bbox_europe <- st_bbox(c(xmin = -10, ymin = 20, xmax = 50, ymax = 80), crs = st_crs(european_union_map))
european_union_map_cropped <- st_crop(european_union_map, bbox_europe)

map <- european_union_map_cropped %>% 
  left_join(map_eu, by = c("name" = "country"))

map.graph <- ggplot(data = map) +
  geom_sf(mapping = aes(fill = avg_score)) +
  scale_fill_gradient(name = "Carbon Emission Score", high = "#FF0000FF", low = "#FFFF00FF", na.value = "grey50")+ 
  ggtitle("Carbon Emission Score Across EU") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

showtable_df = esg_eu_df %>%
  select(TotalReturn_2y, Industry,CARBON_EMISSIONS_SCORE,IVA_COMPANY_RATING, INDUSTRY_ADJUSTED_SCORE,GOVERNANCE_PILLAR_SCORE)

# showing the data frame - important variables 
datatable(showtable_df, options = list(pageLength = 5))
```


#### 1. Correlation Plots

(說明)



```{r corr plots, echo=FALSE, warning=FALSE}
# showing plots
heavy.graph
light.graph
```

#### 2. Avergae Emission Score Across EU

(說明)

```{r map plot, echo=FALSE, warning=FALSE}
map.graph
```





### Modeling 
First, seperate data into carbon heavy industries (those 4), and carbon light industries
I used two models here, linear regression and random forest, you guys can compare the performance of both models


(說明) might want to show how you build model, what varibles you included 



```{r all models, echo=FALSE, warning=FALSE}
#######
# linear regression 
#######
# use 2y as a try, can switch out Y variable, and/or take out "Industry"
lr_heavy = lm(TotalReturn_2y ~ IVA_COMPANY_RATING + INDUSTRY_ADJUSTED_SCORE + GOVERNANCE_PILLAR_SCORE + CARBON_EMISSIONS_SCORE + Industry, data = heavy_train)

lr_light = lm(TotalReturn_2y ~ IVA_COMPANY_RATING + INDUSTRY_ADJUSTED_SCORE + GOVERNANCE_PILLAR_SCORE + CARBON_EMISSIONS_SCORE + Industry, data = light_train, na.action=na.omit)

#######
# random forest
#######

forest_heavy = randomForest(TotalReturn_2y ~ IVA_COMPANY_RATING + INDUSTRY_ADJUSTED_SCORE + GOVERNANCE_PILLAR_SCORE + CARBON_EMISSIONS_SCORE + Industry, data = heavy_train, control = rpart.control(cp = 0.002, minsplit=30), importance = TRUE)

forest_light = randomForest(TotalReturn_2y ~ IVA_COMPANY_RATING + INDUSTRY_ADJUSTED_SCORE + GOVERNANCE_PILLAR_SCORE + CARBON_EMISSIONS_SCORE + Industry, data = light_train, control = rpart.control(cp = 0.002, minsplit=30), importance = TRUE, na.action=na.omit)

# out-of-sample test 
p_heavy<- predict(lr_heavy, heavy_test)
p_light<- predict(lr_light, light_test)

# Compute errors: error
error_heavy <- p_heavy - heavy_test[["TotalReturn_2y"]]
error_light <- p_heavy - heavy_test[["TotalReturn_2y"]]

# Calculate RMSE
rmse_lm_h =sqrt(mean(error_heavy^2))
rmse_lm_l =sqrt(mean(error_light^2))

rmse_forest_h = rmse(forest_heavy, heavy_test) 
rmse_forest_l = rmse(forest_light, light_test) 
```

#### Model Results {.tabset}
##### 1. Linear Model Result

(說明)


```{r model report, echo=FALSE, warning=FALSE}
summary(lr_heavy)
summary(lr_light)
```

##### 2. Random Forest Result


(說明)

```{r model report-2, echo=FALSE, warning=FALSE}
print(forest_heavy)
print(forest_light)
```


##### 3. Compare Out-of-Sample Performance

(說明)
you can use `rmse_lm_h` to show the variable 


```{r rmse, echo=FALSE, warning=FALSE}
rmse_lm_h
rmse_lm_l
rmse_forest_h
rmse_forest_l
```



### Conclusion
(說明)
